Cats and Dogs Recognition

### 2013-12-06 paper.tex
se

\section{Color Feature}
We first normalize all our pictures to be 250px$ \times $250px. This operation will change the ratio of width and height. However, this won't affect results since we are only interested in the color feature of the picture but not the size or shape of the animals. We divide the picture into $n\times n$ square cells with equal size. \\
Then we partition the color spaces. We use two models of color space. The first is RGB color space. A color in the RGB color space is described by indicating how much of the red, green, and blue is included. The color is represented as an RGB triplet $(r, g, b)$. We normalize those three values to be between 0 and 1. 
%(http://en.wikipedia.org/wiki/RGB_color_model#Numeric_representations). 
The second color space is HSV color space. A color is represented as a HSV triplet $(h, s, v)$. The three values are hue, saturation and value. Also, we normalize them to be between 0 and 1. \\
%(http://en.wikipedia.org/wiki/Color_space)
Both of the color spaces are three dimensional. In order to describe our algorithm, we name the three coordinates to be $x, y, z$. We then divide the $x$ coordinate into $N_x$ equal intervals, divide the $y$ coordinate into $N_y$ equal intervals, and divide the $z$ coordinate into $N_z$ equal intervals. As a result, we partition the color space into $N_x \times N_y \times N_z$ cubes. \\
We are now considering two features. The first feature $F_1(i, j)$ is an integer value. We go through all of the pixels inside the $i$-th cell of the picture, and then count the number of pixels whose colors are in the $j$-th cube of the color space. ($ 1 \leq i \leq n^2, 1 \leq j \leq N_x \times N_y \times N_z $), and the count is $F_1(i, j)$. The second feature $F_2(i, j)$ is a boolean value. We still go through all of the pixels inside the $i$-th cell of the picture. If among those pixels, there exists at least one pixel with color in the $j$-th cube of the color space, $F_2(i, j)$ is 1(true); otherwise, $F_2(i, j)$ is 0(false).\\
\begin{table}[h]
\caption{Color Feature Boosting Training Result}
\centering
\begin{tabular}{| l | l | l | l | l | l | l |}
\hline
Color Space Type & n & x & y & z & No. of weak learners & correction rate\\
\hline
RGB($x = r, y = g, z = b$) & 1 & 10 & 10 & 10 & 250 & $60.8 \%$\\
\hline
RGB($x = r, y = g, z = b$) & 3 & 10 & 10 & 10 & 250 & $71.9 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 1 & 10 & 10 & 10 & 250 & $66.8 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 1 & 10 & 10 & 10 & 500 & $66.7 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 3 & 10 & 10 & 10 & 250 & $72.7 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 5 & 10 & 10 & 10 & 250 & $72.7 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 5 & 8 & 8 & 8 & 250 & $72.1 \%$\\
\hline
\end{tabular}
\end{table}
We finally choose to go with $F_2(i, j)$ because in the training pictures, the portion of the animal area varies. To classify a new picture, it makes more sense to check if the picture contains more typical dog colors or more cat colors instead of check the absolute number of pixels with typical dog colors or typical cat colors. \\
We use 10000 pictures to train our classifier. Half of them are dog pictures and half of them are cat pictures. Then we use our classifier to classify 2000 test pictures. Also, half of the test pictures are cats, and the other half are dogs. For each picture, we get a feature vector with length $n^2 N_x N_y N_z$. Then we run boosting algorithm with a logistic loss to train the classifiers and test on our test examples.\\
From Table1, we can see that the highest correction rate we achieve is 72.7 \%, with the feature HSV$(n =3 ,x = 10, y = 10, z = 10)$ or HSV$(n =5 ,x = 10, y = 10, z = 10)$. We can also notice that feature vector generated from HSV color space is better than feature vector from RGB color space.   A possible explanation is that HSV color space is more closer to human perception of color.

\section{Texture Feature}
%(http://en.wikipedia.org/wiki/Image_texture)
Image Texture represents the information about the spatial arragement of colors or intensities within an image. For this problem, we will use MATLAB's built-in Gray-Level Co-Occurence Matrix (GLCM) to analyse a picture's texture. In a $n \times n$ Gray-Level Occurence Matrix $G$, $G(i, j)$ represents how often a pixel with intensity $i$ occurs with an offset to a pixel with intensity $j$. \\
\includegraphics[width = 6cm]{glcm} \\
For example, the above picture shows the intensity level of each pixel in a 6-by-6 pixel images. If we set offset to be $(0,1)$, which means the second pixel is 0 pixel down and 1 pixel left comparing to the first pixel. So a pixel with intensity 3 occurs three times with this offset to a pixel with intensity 2. So $G(3,2) = 3$.\\
To get the GLCM, first, we transform the picture into a gray-level picture. Then each pixel should have its own intensity (gray-level). Then we use scaling to reduce the number of intensity values to be $n$, so we will get an $n \times n$ GLCM. \\
So if we use $N_f$ offsets, we can get $N_f$ GLCMs. If the $o$-th GLCM matrix is $G_o$, our first texture feature $TF_1(o,i,j)$ represents $G_o(i, j)$. \\
To describe the picture's GLCM more accurately, we introduce four parameters, Contrast, Correlation, Energy and Homogeneity. Contrast is a measure of the intensity contrast between two neighbor pixels; Correlation is a measure of how correlated a pixel is to its neighbor; Energy is a measure of the whole image's intensity; Homogeneity is a measure of how close the elements in the GLCM are to the diagonal elements. The formulas are: \\
$$ \mathrm{Contrast} = \sum_{i,j}|i-j|^2 G(i,j) $$
$$ \mathrm{Correlation} = \sum_{i,j}\frac{(i - \mu_i)(j - \mu_j)G(i,j)}{\sigma_i \sigma_j} $$
$$ \mathrm{Energy} = \sum_{i,j}G(i,j)^2 $$
$$ \mathrm{Homogeneity} = \sum_{i,j} \frac{G(i,j)}{1 + |i-j|} $$
Have those four properties, we can get a new feature $TF_2(o, i) (1 \leq i \leq 4)$. $TF_2(o, 1)$, $TF_2(o,2)$, $TF_2(o,3)$, $TF_2(o,4)$ denote $G_o$'s Contrast, Correlation, Energy and Homogeneity separately.\\
We also use the same 10000 pictures to train our classifier. Then we use our classfier to classify the same 2000 test pictures. For each picture, feature vector $TF_1$ has a length of $n^2 \times N_f$ and $TF_2$ has a length of $4 \times N_f$. And by $N_f =15$, the offsets are $(i,j) (0 \leq i, j \leq 3$ \& at least one of $i,j \neq 0)$. By $N_f = 24$, the offsets are $(i,j) (0 \leq i, j \leq 4$ \& at least one of $i,j \neq 0)$. Then we run boosting algorithm with a logistic loss and 250 weak learners to train the classifiers and test on our test examples.\\
From Table2, we can see that all of the classifiers have similar correction rate. The highest correction rate we achieve is 67.1 \%, with the feature TF1$(n =8 ,N_f = 24)$ or TF1$(n =8 ,N_f = 15)$. We can also notice that TF1 feature (using GLCM matrix directly) is better than TF2 feature (using statistics of GLCM).

@@

>>>>

\section{Color Feature}
We first normalize all our pictures to be 250px$ \times $250px, then divide each picture into $n\times n$ square cells with equal size. Then we partition the color spaces. We use both RGB color space and HSV color space. In both of the color spaces, a color is represented by a triplet $(x,y,z)$. We normalize all these three values to be between 0 and 1. We then divide the $x,y,z$ coordinate into $N_x, N_y, N_z$ equal intervals, and the color space is divided into $N_x \times N_y \times N_z$ cubes. \\
We are now considering two features. The first feature $F_1(i, j)$ is an integer value. We go through all of the pixels inside the $i$-th cell of the picture, and then count the number of pixels whose colors are in the $j$-th cube of the color space. ($ 1 \leq i \leq n^2, 1 \leq j \leq N_x \times N_y \times N_z $), and the count is $F_1(i, j)$. The second feature $F_2(i, j)$ is a boolean value. We still go through all of the pixels inside the $i$-th cell of the picture. If among those pixels, there exists at least one pixel with color in the $j$-th cube of the color space, $F_2(i, j)$ is 1(true); otherwise, $F_2(i, j)$ is 0(false).\\
\begin{table}[h]
\caption{Color Feature Boosting Training Result}
\centering
\begin{tabular}{| l | l | l | l | l | l | l |}
\hline
Color Space Type & n & x & y & z & No. of weak learners & correction rate\\
\hline
RGB($x = r, y = g, z = b$) & 1 & 10 & 10 & 10 & 250 & $60.8 \%$\\
\hline
RGB($x = r, y = g, z = b$) & 3 & 10 & 10 & 10 & 250 & $71.9 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 1 & 10 & 10 & 10 & 250 & $66.8 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 1 & 10 & 10 & 10 & 500 & $66.7 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 3 & 10 & 10 & 10 & 250 & $72.7 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 5 & 10 & 10 & 10 & 250 & $72.7 \%$\\
\hline
HSV($x = h, y = s, z = v$) & 5 & 8 & 8 & 8 & 250 & $72.1 \%$\\
\hline
\end{tabular}
\end{table}
We choose to go with $F_2(i, j)$ because in the training pictures, the portion of the animal area varies. To classify a new picture, it makes more sense to check if the picture contains more typical dog colors or more cat colors instead of check the absolute number of pixels with typical dog colors or typical cat colors. \\
We use 10000 pictures to train our classifier, and then test 2000 pictures. We run boosting algorithm with a logistic loss.\\
From Table 1, we can see that the highest correction rate we achieve is 72.7 \%, with the feature HSV$(n =3 ,x = 10, y = 10, z = 10)$ or HSV$(n =5 ,x = 10, y = 10, z = 10)$. We can also notice that feature vector generated from HSV color space is better than feature vector from RGB color space.  A possible explanation is that HSV color space is more closer to human perception of color.

\section{Texture Feature}
\subsection{GLCM}
We use Gray-Level Co-Occurence Matrix (GLCM) to analyse a picture's texture. In an $n \times n$ Gray-Level Occurence Matrix $G$, $G(i, j)$ represents how often a pixel with intensity $i$ occurs with an offset to a pixel with intensity $j$. \\
\includegraphics[width = 6cm]{glcm} \\
For example, the above shows the intensity level of each pixel in a 6-by-6 pixel images. If we set offset to be $(0,1)$, which means the second pixel is 0 pixel down and 1 pixel left comparing to the first pixel. We can see a pixel with intensity 3 occurs three times with this offset to a pixel with intensity 2. So $G(3,2) = 3$.\\
To get the GLCM, first, we transform the picture into a gray-level picture. Then each pixel should have its own intensity (gray-level). Then we use scaling to reduce the number of intensity values to be $n$, so we will get an $n \times n$ GLCM. and if we use $N_f$ offsets, we can get $N_f$ GLCMs. If the $o$-th GLCM matrix is $G_o$, our first texture feature $TF_1(o,i,j)$ represents $G_o(i, j)$. \\
Our second feature $TF_2$ will be the statistics of the GLCM instead of GLCM itself. $TF_2(o, i) (1 \leq i \leq 4)$ represent the $G_o$'s Contrast, Correlation, Energy and Homogeneity separately.
% Contrast is a measure of the intensity contrast between two neighbor pixels; Correlation is a measure of how correlated a pixel is to its neighbor; Energy is a measure of the whole image's intensity; Homogeneity is a measure of how close the elements in the GLCM are to the diagonal elements. 
Their definitions are given below: \\
$$ \mathrm{Contrast} = \sum_{i,j}|i-j|^2 G(i,j) ~~~~
 \mathrm{Correlation} = \sum_{i,j}\frac{(i - \mu_i)(j - \mu_j)G(i,j)}{\sigma_i \sigma_j} $$
$$ \mathrm{Energy} = \sum_{i,j}G(i,j)^2 ~~~~
\mathrm{Homogeneity} = \sum_{i,j} \frac{G(i,j)}{1 + |i-j|} $$
We also use the same 10000 pictures to train our classifier. Then we use our classfier to classify the same 2000 test pictures. For each picture, feature vector $TF_1$ has length $n^2 \times N_f$ and $TF_2$ has length $4 \times N_f$. And by $N_f =15$, the offsets are $(i,j) (0 \leq i, j \leq 3$ \& at least one of $i,j \neq 0)$. By $N_f = 24$, the offsets are $(i,j) (0 \leq i, j \leq 4$ \& at least one of $i,j \neq 0)$. Then we run boosting algorithm with a logistic loss and 250 weak learners.\\
From Table 2, we can see that all of the classifiers have similar correction rate. The highest correction rate we achieve is 67.1 \%, with the feature TF1$(n =8 ,N_f = 24)$ or TF1$(n =8 ,N_f = 15)$. We can also notice that TF1 feature (using GLCM matrix directly) is better than TF2 feature (using statistics of GLCM). One possible explanation is that only four statistics cannot show all the information of the picture. To improve this, we can add more statistics in the future, such as Dissimilarity and Entropy.

@@

\subsection {HOOG}
HOOG is also a good feature to describe a picture's texture. A detailed discription of it is included in section 6.1.2. \\
 WEIXINC!!!
